Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-09-30 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_24_outlierdetection_MK.Rmd
xpaper

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_expert, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for novices
ggplot(df_aoi_sum_novice, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.25)
Q3 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_mtu_nov <- df_aoi_sum_novice %>%
  filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_sum_novice)  # Original data
nrow(df_no_outliers_mtu_nov)  # After removing outliers

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_stud_expert, aes(x = "", y = Stud_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI students)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for novices
ggplot(df_aoi_stud_novice, aes(x = "", y = Stud_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI students)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_disrup_expert, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for novices
ggplot(df_aoi_disrup_novice, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_expert, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of Average duration of fixations",
       y = "Average duration of fixations in msec") +
  theme_minimal()

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_novice, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of Average duration of fixations",
       y = "Average duration of fixations in msec") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_aoi_disrup_expert, aes(x = "", y = Average_duration_disrup)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
       y = "Average duration of fixations") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_aoi_disrup_novice, aes(x = "", y = Average_duration_disrup)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
       y = "Average duration of fixations") +
  theme_minimal()

@@

#### 2.2.7 Gaze Relational Index (GRI; micro-teaching unit)
```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

# GRI = Average_duration_mtu / Sum_number_fixation

@@

### EXPERTS ###
# filter only for experts
df_gri_expert <- df_aoi_sum %>% 
  filter(Group == "Expert")

# Boxplot showing outliers
ggplot(df_gri_expert, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERT: Boxplot average duration (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

# Boxplot showing outliers
ggplot(df_gri_expert, aes(x = "", y = Sum_number_fixation)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERT: Boxplot of summarized number of fixations (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_gri_novice, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICE: Boxplot average duration (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

# Boxplot showing outliers
ggplot(df_gri_novice, aes(x = "", y = Sum_number_fixation)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICE: Boxplot of summarized number of fixations (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_ttff_disrup_novice, aes(x = "", y = Disrup_time_fixation_sec)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICE: Boxplot of time to first fixation in seconds (AOI disruptive person)",
       y = "Time to first fixation in seconds") +
  theme_minimal()

@@

#### ALL #### 
# create data frame without outliers
df_sjt_mean_all_no_out <- df_sjt_mean %>% 
  filter(!Participant %in% c("216", "217", "127"))

@@

#### MANAGING MOMENTUM #### 
# t-test for expertise differences 
t.test(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
       y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_mm <- CohenD(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
                   y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

#### MONITORING ####
# t-test for expertise differences 
t.test(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
       y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_moni <- CohenD(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
                     y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
                     na.rm = TRUE
                    )

@@

#### RULES & ROUTINES #### 
# t-test for expertise differences 
t.test(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
       y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
       var.equal = TRUE
      )

# effect size for expertise differences
d_sjt_rr <- CohenD(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
                   y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

@@

# select relevant columns
df_sjt_mm <- df_sjt %>%
    dplyr::select(WT_S1_F1F2_AL:WT_S4_F4F6_AL)

@@

# select relevant columns
df_sjt_m <- df_sjt %>%
    dplyr::select(WT_S5_F1F2_ST:WT_S9_F4F5_ST)

@@

# select relevant columns
df_sjt_r <- df_sjt %>%
  dplyr::select(WT_S11_F1F5_R:WT_S14_F4F6_R)

@@

@@

# demo data 
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  filter(!LI06_05 == 201,
         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
  transmute(Participant = LI06_05,
            `Teaching Experience` = LI04_01,
            )

# average duration, number fixation, GRI (micro-teaching unit)
df_aoi %>%
  filter(TOI == "Lesson") %>% 
  dplyr::select(
    Duration_of_interval,
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    !"Total_duration_of_fixations.Disruptive_Person",
    !"Number_of_fixations.Disruptive_Person",
    !"Average_duration_of_fixations.Disruptive_Person"
  ) %>%
  rowwise() %>%
  transmute(
    Participant = Participant,
    Duration_of_interval = Duration_of_interval, 
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
    GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)
    ) %>%
  drop_na() %>% 
  filter(!Participant %in% c(216)) %>% 
  dplyr::select(Participant,
         Number_fixation_min_mtu, 
         Average_duration_mtu,
         GRI_mtu) -> df_aoi_numb_dur

# average duration, number fixation, GRI (AOI student)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Participant,
    Duration_of_interval,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Participant = Participant,
    Duration_of_interval = Duration_of_interval,
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
    GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2)
    ) %>% 
  dplyr::select(Participant,
                Stud_number_fixation_min,
                Average_duration_stud,
                GRI_stud) -> df_aoi_stud

# average duration, number fixation, GRI (AOI disruptive person)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(Participant,
                "Total_duration_of_fixations.Disruptive_Person",
                "Number_of_fixations.Disruptive_Person"
                ) %>%
  rowwise() %>%
  mutate(
    Average_duration_disrup = round(
      Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
      digits = 0),
    GRI_disrup = round(
      Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2)) %>% 
  dplyr::select(Participant,
                Number_of_fixations.Disruptive_Person,
                Average_duration_disrup,
                GRI_disrup
                ) -> df_aoi_disrup

# time to first fixatoin (AOI disruptive person)
df_aoi %>%
  filter(
    TOI %in% c(
      "Chatting_with_neighbour",
      "Clicking_pen",
      "Drawing",
      "Drumming_with_hands",
      "Head_on_table",
      "Heckling",
      "Looking_at_phone",
      "Snipping_with_fingers",
      "Whispering"
    )
  ) %>%
  dplyr::select(Participant, TOI, Time_to_first_fixation.Disruptive_Person, ) %>%
  rowwise() %>%
  drop_na() %>%
  group_by(Participant) %>%
  summarise(
    Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person)
  ) %>%
  mutate(
    Group = ifelse(Participant < 200, "Novice", "Expert"),
    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000,
      digits = 2
    )
  ) -> df_ttff_disrup

# rating scales
df_sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201,
               223),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>% 
  rename(Participant = ID) %>%
  group_by(Participant) %>% 
  summarise(
    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
    )%>% 
  dplyr::select(Participant,
                Mean_disrupption_appraisal,
                Mean_confidence_appraisal,
                Mean_prevalence_rating)

# sjt
df_sjt <-
  read_excel("./data/SJT.xlsx") %>%
  dplyr::select(UI06_05, # Participant
                SJT_AL_gek, # Monitoring
                SJT_ST_gek, # Managing momentum
                SJT_R_gek, # Rules and routines
                SJT_KF_gek) %>% # All
  filter(!UI06_05 %in% c(201, 223, 216)) %>%  # exclude ID with no eye tracking data
  transmute(
    Participant = UI06_05,
    SJT_Monitoring = round(SJT_AL_gek, 2),
    SJT_Managing_momentum = round(SJT_ST_gek, 2),
    SJT_Rules_routines = round(SJT_R_gek, 2),
    SJT_All = round(SJT_KF_gek, 2)
    ) %>% 
    arrange(Participant)

# classroom questionnaire
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
                LP01_01:LP01_08) %>% # non- & paraverbal communication
  filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
  rename(Participant = LI06_05) %>%
  group_by(Participant) %>%
  transmute(
    Participant = Participant,
    "Quest_All" = round(mean(c_across(starts_with(
      "L"
    )), na.rm = TRUE), 2),
    "Quest_classroom_management" = round(mean(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2)
  )

# create a big data frame with all measures 
# put all data frames into list
df_list <- list(df_demo,
                df_aoi_numb_dur,
                df_aoi_stud,
                df_aoi_disrup,
                df_sri,
                df_sjt,
                df_quest)

# merge all data frames in list
df_merge <-
  df_list %>% reduce(full_join, by='Participant') %>%
  arrange(Participant) %>% 
  # filter(!Participant %in% c(216)) %>% 
  dplyr::select(.,
                -"Participant",
                -"Teaching Experience")

# create a correlation matrix
cor_tab <- 
  df_merge %>% 
  cor(method = "pearson") %>% 
  round(., digits = 2)

# p-value for GRI x STJ_All
cor.test(df_aoi_numb_dur$GRI_mtu, df_sjt$SJT_All)
cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)

# teaching experience only with experts
df_merge_teaching_experience <-
  df_list %>% reduce(full_join, by='Participant') %>%
  filter(Participant > 200) %>% 
  dplyr::select(.,
                -"Participant")

>>>>

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_expert, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for novices
ggplot(df_aoi_sum_novice, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_stud_expert, aes(x = "", y = Stud_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of number of fixations per minute (AOI students)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for novices
ggplot(df_aoi_stud_novice, aes(x = "", y = Stud_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of number of fixations per minute (AOI students)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_disrup_expert, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of number of fixations per minute (AOI disruptive person)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for novices
ggplot(df_aoi_disrup_novice, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of number of fixations per minute (AOI disruptive person)",
       y = "Number of fixations per minute") +
  theme_minimal()

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_expert, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of Average duration of fixations",
       y = "Average duration of fixations in msec") +
  theme_minimal()

@@

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_novice, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of Average duration of fixations",
       y = "Average duration of fixations in msec") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_aoi_disrup_expert, aes(x = "", y = Average_duration_disrup)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of average duration of fixations (AOI disruptive person)",
       y = "Average duration of fixations") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_aoi_disrup_novice, aes(x = "", y = Average_duration_disrup)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of average duration of fixations (AOI disruptive person)",
       y = "Average duration of fixations") +
  theme_minimal()

@@

#### 2.2.7 Gaze Relational Index (GRI; micro-teaching unit)

GRI = Average duration of fixations (mtu) / Sum number of fixations (mtu)

```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

@@

# filter only for experts
df_gri_expert <- df_aoi_sum %>% 
  filter(Group == "Expert")

# Boxplot showing outliers
ggplot(df_gri_expert, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot average duration (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

# Boxplot showing outliers
ggplot(df_gri_expert, aes(x = "", y = Sum_number_fixation)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of summarized number of fixations (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_gri_novice, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot average duration (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

# Boxplot showing outliers
ggplot(df_gri_novice, aes(x = "", y = Sum_number_fixation)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of summarized number of fixations (mtu)",
       y = "Mean duration of fixations/\nmean number of fixations") +
  theme_minimal()

@@

# Boxplot showing outliers
ggplot(df_ttff_disrup_novice, aes(x = "", y = Disrup_time_fixation_sec)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of time to first fixation in seconds (AOI disruptive person)",
       y = "Time to first fixation in seconds") +
  theme_minimal()

@@

#### ALL ####

# create data frame without outliers
df_sjt_mean_all_no_out <- df_sjt_mean %>% 
  filter(!Participant %in% c("216", "217", "127"))

@@

#### MANAGING MOMENTUM ####

# create data frame without outliers
df_sjt_mean_mm_no_out <- df_sjt_mean %>% 
  filter(!Participant %in% c("105", "127"))

# t-test for expertise differences 
t.test(x = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Expert"],
       y = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_mm <- CohenD(x = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Expert"],
                   y = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

#### MONITORING ####

# create data frame without outliers
df_sjt_mean_m_no_out <- df_sjt_mean %>% 
  filter(!Participant %in% c("121", "127", "137"))

# t-test for expertise differences 
t.test(x = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Expert"],
       y = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_moni <- CohenD(x = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Expert"],
                     y = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Novice"],
                     na.rm = TRUE
                    )

@@

#### RULES & ROUTINES ####

# create data frame without outliers
df_sjt_mean_r_no_out <- df_sjt_mean %>% 
  filter(!Participant %in% c("127"))

# t-test for expertise differences 
t.test(x = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Expert"],
       y = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Novice"],
       var.equal = TRUE
      )

# effect size for expertise differences
d_sjt_rr <- CohenD(x = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Expert"],
                   y = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

# read in data
df_sjt_no_out <-
  read_excel("./data/SJT.xlsx")

### ALL
df_sjt_all <- df_sjt_no_out %>% 
  dplyr::select(WT_S1_F1F2_AL:WT_S14_F4F6_R)

# calculate omega with omega() function  
df_sjt_all <- omega(df_sjt_all)

# display the results 
print(df_sjt_all)

@@

# select relevant columns
df_sjt_mm <- df_sjt_no_out %>%
    dplyr::select(WT_S1_F1F2_AL:WT_S4_F4F6_AL)

@@

# select relevant columns
df_sjt_m <- df_sjt_no_out %>%
    dplyr::select(WT_S5_F1F2_ST:WT_S9_F4F5_ST)

@@

# select relevant columns
df_sjt_r <- df_sjt_no_out %>%
  dplyr::select(WT_S11_F1F5_R:WT_S14_F4F6_R)

@@

# calculate omega with omega() function  
df_quest <- omega(df_quest)

# display the results 
print(df_quest)

@@

# # demo data 
# df_demo <- 
#   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
#   filter(!LI06_05 == 201,
#          !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
#   transmute(Participant = LI06_05,
#             `Teaching Experience` = LI04_01,
#             ) %>% 
#   filter(!Participant %in% c("216", "217", "127", "105", "121", "137")) # filter SJT outlier
# 
# 
# # average duration, number fixation, GRI (micro-teaching unit)
# df_aoi %>%
#   filter(TOI == "Lesson") %>% 
#   dplyr::select(
#     Duration_of_interval,
#     Participant,
#     starts_with("Total_duration_of_fixations"),
#     starts_with("Number_of_fixations"),
#     starts_with("Average_duration"),
#     !"Total_duration_of_fixations.Disruptive_Person",
#     !"Number_of_fixations.Disruptive_Person",
#     !"Average_duration_of_fixations.Disruptive_Person"
#   ) %>%
#   rowwise() %>%
#   transmute(
#     Participant = Participant,
#     Duration_of_interval = Duration_of_interval, 
#     Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
#     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
#     Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
#     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
#     Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
#     Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
#     GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)
#     ) %>%
#   drop_na() %>% 
#   filter(!Participant %in% c(216)) %>% 
#   filter(!Participant %in% c("216", "217", "127", "105", "121", "137")) %>%  # filter SJT outlier
#   filter(!Participant %in% c("205")) %>%  # filter GRI outlier
#   dplyr::select(Participant,
#          Number_fixation_min_mtu, 
#          Average_duration_mtu,
#          GRI_mtu) -> df_aoi_numb_dur
# 
# 
# # average duration, number fixation, GRI (AOI student)
# df_aoi %>%
#   filter(TOI == "Lesson") %>%
#   dplyr::select (
#     Participant,
#     Duration_of_interval,
#     "Total_duration_of_fixations.Anna",
#     "Total_duration_of_fixations.Bianca",
#     "Total_duration_of_fixations.Carl(a)",
#     "Number_of_fixations.Anna",
#     "Number_of_fixations.Bianca",
#     "Number_of_fixations.Carl(a)"
#   ) %>%
#   rowwise() %>%
#   transmute(
#     Participant = Participant,
#     Duration_of_interval = Duration_of_interval,
#     Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
#     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
#     Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
#     Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
#     Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
#     GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2)
#     ) %>%
#   dplyr::select(Participant,
#                 Stud_number_fixation_min,
#                 Average_duration_stud,
#                 GRI_stud) -> df_aoi_stud
# 
# 
# # average duration, number fixation, GRI (AOI disruptive person)
# df_aoi %>%
#   filter(TOI == "Lesson") %>%
#   dplyr::select(Participant,
#                 "Total_duration_of_fixations.Disruptive_Person",
#                 "Number_of_fixations.Disruptive_Person"
#                 ) %>%
#   rowwise() %>%
#   mutate(
#     Average_duration_disrup = round(
#       Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
#       digits = 0),
#     GRI_disrup = round(
#       Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2)) %>%
#   dplyr::select(Participant,
#                 Number_of_fixations.Disruptive_Person,
#                 Average_duration_disrup,
#                 GRI_disrup
#                 ) -> df_aoi_disrup
# 
# # time to first fixation (AOI disruptive person)
# df_aoi %>%
#   filter(
#     TOI %in% c(
#       "Chatting_with_neighbour",
#       "Clicking_pen",
#       "Drawing",
#       "Drumming_with_hands",
#       "Head_on_table",
#       "Heckling",
#       "Looking_at_phone",
#       "Snipping_with_fingers",
#       "Whispering"
#     )
#   ) %>%
#   dplyr::select(Participant, TOI, Time_to_first_fixation.Disruptive_Person, ) %>%
#   rowwise() %>%
#   drop_na() %>%
#   group_by(Participant) %>%
#   summarise(
#     Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person)
#   ) %>%
#   mutate(
#     Group = ifelse(Participant < 200, "Novice", "Expert"),
#     Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000,
#       digits = 2
#     )
#   ) -> df_ttff_disrup
# 
# # rating scales
# df_sri <-
#   excel_sheets("data/Coding_SRI.xlsx") %>%
#   map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
#   filter(
#     !ID %in% c(201,
#                223),
#     !disruption_appraisal == -100,
#     !confidence_appraisal == -100,
#     !disruption_appraisal == -99,
#     !confidence_appraisal == -99,
#     !disruption_appraisal == -88,
#     !confidence_appraisal == -88,
#     !prevalence_rating == -100,
#     !prevalence_rating == -99,
#     !prevalence_rating == -88
#     ) %>% 
#   rename(Participant = ID) %>%
#   group_by(Participant) %>% 
#   summarise(
#     Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
#     Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
#     Mean_prevalence_rating = round(mean(prevalence_rating), 2)
#     )%>% 
#   dplyr::select(Participant,
#                 Mean_disrupption_appraisal,
#                 Mean_confidence_appraisal,
#                 Mean_prevalence_rating)
# 
# # sjt
# df_sjt <-
#   read_excel("./data/SJT.xlsx") %>%
#   dplyr::select(UI06_05, # Participant
#                 SJT_AL_gek, # Monitoring
#                 SJT_ST_gek, # Managing momentum
#                 SJT_R_gek, # Rules and routines
#                 SJT_KF_gek) %>% # All
#   filter(!UI06_05 %in% c(201, 223, 216)) %>%  # exclude ID with no eye tracking data
#   filter(!UI06_05 %in% c("216", "217", "127", "105", "121", "137")) %>%  # filter SJT outlier
#   filter(!UI06_05 %in% c("205")) %>%  # filter GRI outlier
#   transmute(
#     Participant = UI06_05,
#     SJT_Monitoring = round(SJT_AL_gek, 2),
#     SJT_Managing_momentum = round(SJT_ST_gek, 2),
#     SJT_Rules_routines = round(SJT_R_gek, 2),
#     SJT_All = round(SJT_KF_gek, 2)
#     ) %>% 
#     arrange(Participant)
# 
# # classroom questionnaire
# df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
#   dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
#                 LP01_01:LP01_08) %>% # non- & paraverbal communication
#   filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
#   rename(Participant = LI06_05) %>%
#   group_by(Participant) %>%
#   transmute(
#     Participant = Participant,
#     "Quest_All" = round(mean(c_across(starts_with(
#       "L"
#     )), na.rm = TRUE), 2),
#     "Quest_classroom_management" = round(mean(c_across(starts_with(
#       "LM"
#     )), na.rm = TRUE), 2),
#     "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
#       "LP"
#     )), na.rm = TRUE), 2)
#   )
# 
# # create a big data frame with all measures 
# # put all data frames into list
# df_list <- list(df_demo,
#                 df_aoi_numb_dur,
#                 df_aoi_stud,
#                 df_aoi_disrup,
#                 df_sri,
#                 df_sjt,
